---
title: "Attrition and Reasons"
author: "Langyi Tian and Jay Souder"
date: "July 2019"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "custom_Xaringan.css"]
    lib_dir: libs
    keep_md: true
    self_contained: false
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      countdown: 120000
editor_options: 
  chunk_output_type: inline
---
exclude: true

class: left, top
background-size: 100%
background-position: 50% 280%

```{r setup, include=FALSE}
rm(list = ls())#clear environment
wd <- "~/GitHub/Pet-projects/TCC_pet_project/"#set working directory
#Set up default knitr chunk options
library("knitr")
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.height = 7,
  fig.width = 15,
  fig.align = "center",
  cache = TRUE,
  cache.lazy = FALSE
)
options(htmltools.dir.version = FALSE)
```  

```{r theme-map, include=FALSE}
#set up theme map for presentation
theme_simplemap <- function(base_size = 9,
                            base_family = "") {
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      axis.line = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank(),
      panel.grid = element_blank(),
      panel.spacing = unit(0, "lines"),
      plot.background = element_blank(),
      legend.position = "none"
    )
}
```

```{r load packages}
#load packages.
packages <- c(
  "pkgnet",
  "praise",
  "tidyverse",
  "knitr",
  "ggplot2",
  "plotly",
  "widgetframe",
  "gridExtra",
  "ggmap",
  "RColorBrewer",
  "jtools",
  "ggstance",
  "ggraph",
  "igraph"
)
packages <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x)
      library(x, character.only = TRUE)
    }
  }
)
#avoid func name conflict
select<-dplyr::select
```

```{r paths}
#fix token paths and system parameters
tokens <- read.csv("tokens.csv",
                   stringsAsFactors = FALSE)
Sys.setenv(
  #plotly
  plotly_username = tokens$key[tokens$tokenname == "plotly_username"],
  plotly_api_key = tokens$key[tokens$tokenname == "plotly_api_key"],
  #aws s3
  AWS_ACCESS_KEY_ID = tokens$key[tokens$tokenname == "AWS_ACCESS_KEY_ID"],
  AWS_SECRET_ACCESS_KEY = tokens$key[tokens$tokenname == "AWS_ACCESS_KEY_ID"],
  AWS_DEFAULT_REGION = "us-east-2"
)
```

```{r}
#import data
#list all files in data storage
dta_processed_list <-
  list.files(
    "dta_processed",
    pattern = "*.RData",
    full.names = TRUE
  )
#load them
for (i in dta_processed_list){
  load(i)
}
```

---
## Year Hired for Current TCC Population
```{r current cohort, fig.height = 5, fig.width = 10, fig.align = "center"}
#prepare data for pie chart on hiring
pie_cohort <-
  dta_merged %>%
  filter(terminated == FALSE) %>% #active people
  select(name, hire_date) %>% #keep name and time hired
  mutate(
    hire_date = hire_date %>%
      as.Date() %>%
      cut("year") %>%
      as.character() %>%
      str_extract("^[:digit:]{4}") #extract year of hire
  ) %>%
  group_by(hire_date) %>% #group people by year
  summarise(freq = n())

#make pie chart of current cohort
plot_pie_cohort <-
  ggplot(pie_cohort,
         aes(x = "",
             y = freq,
             fill = hire_date)) +
  #bar plot
  geom_bar(stat = "identity",
           color = "seashell4") +
  #set text to be size of cohort
  geom_text(
    aes(label = paste(freq)),
    color = "gray16",
    position = position_stack(vjust = 0.5),
    size = 5.5
  ) +
  coord_polar(theta = "y", start = 0) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(caption = "Current size 187",
       fill = "Year Hired") +
  theme_void() +
  theme(text = element_text(size = 20))

plot_pie_cohort
```

 - A majority of the current population has less than 6 months of experience, and avg. QA score of 81%
 
 - Agents hired before 2018 have an avg. QA score of 89% over time
 
 - Effect on training, performance
 
???

 - Refresh audience about how young current population is, and resulting performance differences
 - hiring several centers worth of agents

---
## A Few Groups Drive the Attrition Since 2018
```{r fig.height = 7, fig.width = 15, fig.align = "center"}
#make data on tenure by group
tenure_by_group <-
  dta_merged %>%
  filter(is.na(group) == FALSE,
         group != "Training") %>% #keep common groups
  group_by(group, terminated) %>%
  summarise(
    num = n(),
    qa_mean = mean(qa_mean, na.rm = TRUE),
    tenure = mean(tenure, na.rm = TRUE)
  ) %>% #summary performance and tenure by group
  mutate(
    num = ifelse(terminated == TRUE,
                 num * -1,
                 num),
    terminated = terminated %>%
      as.numeric() %>%
      recode(`0` = "Active",
             `1` = "Terminated")
  ) #make settings for pyramid plot

#plot pyramid plot
plot_tenure_group <-
  ggplot(tenure_by_group,
         aes(
           x = group %>% reorder(-num),
           y = num,
           fill = terminated
         )) +
  #make both sides of the pyramid
  geom_bar(data = tenure_by_group %>%
             filter(terminated == "Terminated"),
           stat = "identity") +
  geom_bar(data = tenure_by_group %>%
             filter(terminated == "Active"),
           stat = "identity") +
  #set up axis
  scale_y_continuous(breaks = seq(-100, 50, 5),
                     labels = c(seq(100, 0,-5),
                                seq(5, 50, 5))) +
  #pretty the plot
  scale_fill_brewer(palette = "Dark2",
                    direction = 1) +
  coord_flip(expand = TRUE) +
  xlab("") +
  ylab("") +
  labs(fill = "Status") +
  theme_classic() +
  theme(text = element_text(size = 20))

plot_tenure_group
```

???
 - Care still making up most of the attrition
 
---
## Top Exiting Reasons in Client Groups
```{r}
#extract unique group names
group_names <- dta_merged$group[is.na(dta_merged$group) == FALSE &
                           dta_merged$group != "Training"] %>% unique()
#a function loop to make plot showing top exiting reasons
attrition_pie <- NULL
for (i in group_names) {
  #extract top exit reasons for each group
  dta <- dta_merged %>%
    filter(group == i,
           is.na(reason_detail) == FALSE) %>%
    group_by(reason = reason_detail) %>%
    summarise(Freq = n()) %>%
    arrange(-Freq) %>%
    top_n(3)
  #make the pie plot
  attrition_pie[[i]] <- ggplot(dta,
                               aes(
                                 x = "",
                                 y = Freq,
                                 fill = reason %>%
                                   fct_reorder(Freq, .fun = max)
                               )) +
    geom_bar(stat = "identity",
             color = "seashell4") +
    #visualize the reason on plot
    geom_text(
      aes(label = paste(Freq)),
      color = "gray16",
      position = position_stack(vjust = 0.5),
      size = 5.5
    ) +
    #pit chart settings
    coord_polar(theta = "y",
                start = 0) +
    scale_fill_brewer(palette = "YlOrRd",
                      direction = 1,
                      labels = dta$reason) +
    labs(caption = paste(i),
         fill = "") +
    theme_void() +
    theme(text = element_text(size = 15))
}
#arrange pie plot for all groups
grid.arrange(
  attrition_pie[[1]],
  attrition_pie[[2]],
  attrition_pie[[3]],
  attrition_pie[[4]],
  attrition_pie[[5]],
  attrition_pie[[6]],
  attrition_pie[[8]],
  attrition_pie[[9]],
  attrition_pie[[10]]
)

```


 - See Appendix 1 for an interactive breakdown of terminated agents

???
 - Consistent theme in leaving reasons: QA performance, job abandonment
 - Banyan has positive attrition, which is what we want to see

---
 

##Factors Impacting Senior Agents' Tenure
```{r}
#modeling
#make a formula to try
tenure_formulate<-formula(tenure ~ age + gender + commute_time + qa_mean_w4 + min + gap + supe)
#model for senior agents
lm_old <-
  lm(tenure_formulate,
     data = dta_merged %>% 
       filter(hire_date %>% 
                as.Date() < "2018-01-01"))
#model for new agents
lm_new <-
  lm(tenure_formulate,
     data = dta_merged %>% 
       filter(hire_date %>% 
                as.Date() > "2018-01-01"))
```

 - Senior agents average profile: 89% on tenure QA, 30 months of tenure

```{r, fig.height = 4, fig.width = 15, fig.align = "center"}
#visualize coefficients on demographics
jtools::plot_summs(
  lm_old,
  lm_new,
  coefs = c(
    "Commute time (min)" = "commute_time",
    "Agent age (year)" = "age",
    "QA Average in first 4 weeks (point)" = "qa_mean_w4",
    "Tenure QA lowest score (point)" = "min",
    "Largest successive decline in QA (point)" = "gap"
  ),
  legend.title = "Population",
  model.names = c("Senior agents",
                  "New hires"),
  
  ci_level = 0.5) +
  scale_x_continuous(breaks = seq(-1.5, 2, by = 0.5)) +
  xlab("Additional impact on agent tenure (month)") +
  ylab("") +
  theme_classic() +
  theme(text = element_text(size = 20))
```

???
Look at factors impacting tenure, diferent in the life cycle of agents 

 - Overall, at early stage of tenure supervisors are decisive to agents' period to stay.
 
 - Agent stays longer in the company had supervisor's effect decreases and other factors showing effect.
 
Senior agents first.

 - Profile: 89% on tenure QA, 30 months of tenure

 - Commute time: Each additional 10 mins bring down tenure by 2.5 month for senior agents

 - Age: additional 4 years in age would add 3 months to likelihood to stay than younger counterparts
 
  - Potential ask: how does the age fit with the push to hire young people?

 - QA: Senior agents with better performance in their early tenure and consistency in scores tend to stay longer
 
 - Past profile does not exactly have to apply (older agents)
 
Rather, these factors are not influential for new hires

---
 

##Supervisors' Influence on New Hires' Tenure
 - New hires average profile: 83% on tenure QA, 3 months of tenure
```{r, fig.height = 7, fig.width = 15, fig.align = "center"}
#visualize coefficients on supervisors
jtools::plot_summs(
  lm_old,
  lm_new,
  coefs = c(
    "Male agents (compared with female)" = "genderM",
    "Ariel Stillman" = "supeAriel Stillman",
    "Carla Martin" = "supeCarla Martin",
    "Devon Gilliam" = "supeDevon Gilliam",
    "Donovan Tucker" = "supeDonovan Tucker",
    "Gia Weinberger" = "supeGia Weinberger",
    "Jeff Mahady" = "supeJeff Mahady",
    "Marie Jenkins" = "supeMarie Jenkins",
    "Megan Stanko" = "supeMegan Stanko",
    "Naila Butt" = "supeNaila Butt",
    "Ray Davis" = "supeRay Davis",
    "Shamala Turner" = "supeShamala Turner"
  ),
  legend.title = "Population",
  model.names = c("Senior agents",
                  "New hires"),
  
  ci_level = 0.5) +
  scale_x_continuous(breaks = seq(-40, 20, by = 5)) +
  labs(caption = "All supervisors compared with Alison Herman") +
  xlab("Additional impact on agent tenure (month)") +
  ylab("") +
  theme_classic() +
  theme(text = element_text(size = 20))
```

???

Clear predictors of new-hire tenure: Supervisor
 
 - Difference can be 6 months on average on everyone, even after considering agents have different QA, age, commute time...
 
 - Short and precise dots for new hires show the effects are significant across all supervisors

After longer tenure, the effect from supervisors are reduced
 
 - Next findings give an overview

---
 

##Certain Supervisors Are Better at Retaining Agents
```{r fig.height = 7, fig.width = 15, fig.align = "center"}
#make data for plotting tenure against supverisor
qa_supe <-
  dta_merged %>%
  filter(is.na(supe) == FALSE,
         hire_date %>% as.Date() > "2018-01-01") %>%  #keep only agent staying relatively for long
  mutate(terminated = terminated %>%
           as.numeric() %>%
           recode(`0` = "Active",
                  `1` = "Terminated"))  #minor change on terminate label
#make tenure labels with numbers
#extract average performance and tenure under each supervisor
tenures <-
  qa_supe %>%
  group_by(supe) %>%
  summarise(tenure = tenure %>% median(na.rm = TRUE),
            qa_mean = qa_mean %>% median(na.rm = TRUE)) %>%
  arrange(tenure) %>%
  mutate(label = paste(supe,
                       ": ",
                       tenure %>%
                         round(digits = 1)))#make the number their label
#set plot properties
colourCount <- length(unique(qa_supe$supe))
getPalette <- colorRampPalette(brewer.pal(9, "RdBu"))
#make plot
plot_tenure_supe_box <- ggplot(
  qa_supe,
  aes(
    x = supe %>%
      fct_reorder(tenure, .fun = median),#recorder by supervisor names by median tenure
    y = tenure,
    fill = supe %>%
      fct_reorder(tenure, .fun = median),
    color = terminated
  )
) +
  #make box plot
  geom_boxplot(color = "black",
               outlier.shape = NA) +
  scale_fill_manual(values = getPalette(colourCount),
                    labels = tenures$label) +
  xlab("") +
  ylab("Average Tenure") +
  labs(color = "Status",
       fill = "Average Tenure",
       caption = "Agents hired after 2018-01-01") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

plot_tenure_supe_box +
  theme(text = element_text(size = 20)) +
  geom_jitter()
```


```{r}
#make interactive plot
plot_tenure_supe_box <- 
  plot_tenure_supe_box +
  #add additional label in interactive plot
  geom_jitter(size = 1,
              aes(
                text = paste(name,"\n",
                  "Age: ",age %>% round(digits = 0),"\n",
                  "Group: ",group,"\n",
                  "Supervisor: ",supe,
                  "(",supe_time,"months total)","\n",
                  "Hired at: ",hire_date,"\n",
                  "Status: ",terminated,"\n",
                  "Tenure QA:",qa_mean %>% round(digits = 0),"%","\n",
                  "Tenure: ",tenure %>% round(digits = 1),"months","\n",
                  "Reason: ",reason_detail,"\n",
                  "---raw codes below-------------"
                )
              )) +
  theme(legend.position = 'none')
#make plotly chart and return api
plot_tenure_supe_box_api <- api_create(
  plot_tenure_supe_box %>%
    plotly::ggplotly(height = 400,
                     width = 1100),
  filename = "plot_tenure_supe_box",
  sharing = "secret"
)
#attach plotly link to the slide
cat(paste(
  "Interactive plot at",
  paste(
    plot_tenure_supe_box_api$web_url %>% str_replace("/$", "?share_key="),
    plot_tenure_supe_box_api$share_key,
    sep = ""
  )
))
```

???

 - This is for agents hired after 1-1-2018

 - The gap can be as large as 6 months
 
Ask: what do good supervisors do differently than low performing supes for retaining agents?
 
 - More active people over the right, which is desirable
 
 - Interactive plot available with agent profiles

---
 

##Target Recruitment Efforts Geographically

```{r commute distance, message=FALSE, warning=FALSE, echo=FALSE, fig.height = 7, fig.width = 15, fig.align = "center"}
#make commute data
commute <-
  dta_merged %>%
  mutate(old = tenure > 10) %>% 
  group_by(commute_start) %>%
  summarise(
    num = n(),
    old = 100 * sum(old, na.rm = TRUE) / n(),
    commute_time = mean(commute_time, na.rm = TRUE),
    tenure = mean(tenure, na.rm = TRUE),
    mode = commute_mode[1]
  ) %>% #make some variables
  #replace some wrongly specified names
  mutate(commute_start = commute_start %>% 
           str_replace_all("COCKYSVIL", "Cockeysville") %>%
           str_replace_all("LUTHVLE TIMON", "Lutherville-Timonium")
         )
#make commute plot
plot_commute <- ggplot(
  commute %>%
    filter(commute_time < 100,
           tenure < 30,
           is.na(mode) == FALSE),
  aes(
    x = commute_time,
    y = tenure,
    size = num,
    color = old,
    text = commute_start
  )
) +
  geom_point() +
  #display city names with good population and good tenure
  geom_text(
    data = commute %>% filter(num > 10 | (commute_time < 20 & tenure < 30 & tenure > 10)),
    aes(label = commute_start),
    position = position_jitter(width = 0.1, height = 0.1),
    color = "black",
    size = 4,
    hjust = -0.2,
    vjust = -0.2
  ) +
  #pretty the plot
  scale_size_continuous(range = c(1.5, 25),
                        guide = "none") +
  scale_color_gradient(low = "darkseagreen1", high = "cyan4") +
  xlab("Commute time (minutes)") +
  ylab("Tenure (months)") +
  labs(color = "% agents > 10 mo") +
  theme_classic() +
  theme(text = element_text(size = 20))

plot_commute
```

???
 - Considerable sample is from Baltimore City, with long commute time and undesirable avg. tenure
 
 - Rather, those who take less than half an hour to work tend to stay longer
 
 - Add value in other ways rather college concentration
