---
title: "Social historical determinants of elder leisure consumption"
author: "Langyi Tian and Aurelien Boucher"
output: html_document
---

## Low-cost leisure and the hysteresis of habitus: An inquiry on elderly leisure in China
This project uses a nationally representative data from China to look at the determinants of elder's consumption. The central point of focus is age, and the socio-historical context in the age gaps. I work with Dr. Aurelien Boucher on this project.

Technically, this is my personal try to use package Statamarkdown to integrate functionalities of Stata with R.

## Abstract
This article investigates into the economic scarcity and social context that have shaped the leisure activities of Chinese elderly consumers through the theory of practice. It aims to demonstrate that elderly in China are less eager to spend money on their leisure and travel activities due to not only present constraints but also a hysteresis of their habitus. A micro-level ethnographic observation and a national survey analysis together would underline how elderly generations grew up under the Maoist period draw the frontier between necessary, desirable and excess consumption. By addressing this matter, this article would challenge the oversimplified justification for a highly potential grey market in China, as well as highlight some key social symptoms in the reform era.

## Keywords
China, elderly, leisure, consumption, habitus, generation

```{r setup, include=FALSE}
#Set up default knitr chunk options
library("knitr")
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.height = 10,
  fig.width = 16,
  fig.align = "center"
)
```  

Stata Setup

```{r call stata}
library(Statamarkdown)
```

## Data preparation
The research question is about what are the determinants of leisure consumption.

This section works for some necessary processing to gather data from a household survey. For the question we look at, we need individual demographic and socio-economic status indicators. We get them from individual and family data set. 

### Data import and merge

Import and modify adult dataset, ready to merge into family dataset

```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
use if urban16==1 using "data\ecfps2016adult_201906.dta", clear
rename pid resp1pid
rename cfps_age age
rename cfps_gender gender
rename cfps2016edu education
rename qg303code_egp egp
rename qg303code_isei isei
rename pa301 hukou
rename qn4001 party
rename fml2016_count familysize
save "data\adult_temp.dta", replace
```

left join family and adult data set, save
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
use if urban16==1 using "data\ecfps2016famecon_201807.dta", clear
merge m:m resp1pid using "data\adult_temp.dta", keepusing(resp1pid age gender education egp isei hukou party familysize)
keep if _merge==3
save "data\family_merged.dta", replace
```

### Engineer some attributes
keep only urban residents
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
use if urban16==1 using "data\family_merged.dta", clear
```

generate features related to leisure, travel, dressing and beauty
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
rename fp502 leisure
rename fp503 travel
rename dress dressing
rename fp513 beauty

*generate expenses on leisure, travel, dressing and beauty

foreach var of varlist leisure travel dressing beauty {
  recode `var' min/-1=. //recode missing value
  gen `var'_pr = (100 * `var') / pce //generate percentage of total expense
  recode `var'_pr 100/max=100 //create censorship
  summarize `var' `var'_pr //check outcome
}

*create total expense of the four items

gen allvalue= leisure + travel
gen allpr= leisure_pr + travel_pr
summarize allvalue allpr
```

 - generate variables indicating real estate value of a household 
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
foreach var of varlist fq6 fr2 {
  
*for the property they live in
  
  recode `var' -8=0 //recode zero value
  recode `var' -2=. -1=. //recode missing value
  
*for other properties
  
  recode `var'_est -8=0
  recode `var'_est -2=. -1=.
  replace `var' = `var'_est if `var'==.
  summarize `var' `var'_est
}

*generate total value of housing asset

gen homevalue=.
replace homevalue=fq6 if fq6!=.
replace homevalue=fq6 + fr2 if fr2!=.
summarize homevalue
```

add control variable: privincial level gdp per capita in 2016
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
gen gdp=16278 if provcd16==11
replace gdp=17131 if provcd16==12 //Tianjin
replace gdp=6509 if provcd16==13 //Hebei
replace gdp=5709 if provcd16==14 //Shanxi
replace gdp=11566 if provcd16==15  //Neimeng
replace gdp=10614 if provcd16==21 //Liaoning
replace gdp=8166 if provcd16==22 //Jilin
replace gdp=6386 if provcd16==13 //Heilongjiang
replace gdp=15851 if provcd16==31 //Shanghai
replace gdp=13328 if provcd16==32 //Jiangsu
replace gdp=11884 if provcd16==33 //Zhejiang
replace gdp=5604 if provcd16==34 //Anhui
replace gdp=10333 if provcd16==35 //Fujian
replace gdp=5645 if provcd16==36 //Jiangxi
replace gdp=9911 if provcd16==37 //Shandong
replace gdp=6035 if provcd16==41 //Henan
replace gdp=7675 if provcd16==42 //Hubei
replace gdp=6556 if provcd16==43 //Hunan
replace gdp=10332 if provcd16==44 //Guangdong
replace gdp=5387 if provcd16==45 //Guangxi
replace gdp=6337 if provcd16==46 //Hainan
replace gdp=7790 if provcd16==50 //Chongqin
replace gdp=5719 if provcd16==51 //Sichuan
replace gdp=4304 if provcd16==52 //Guizhou
replace gdp=4438 if provcd16==53 //Yunan
replace gdp=7640 if provcd16==61 //Shanxi
replace gdp=4303 if provcd16==62 //Gansu
replace gdp=6810 if provcd16==64 //Ningxia
replace gdp=6617 if provcd16==65 //Xinjiang
summarize gdp
```

rename a few other variables

```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
rename fincome1 income
```

Final feature engineering
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
gen allvalue_flag = 1 if allvalue>0
replace allvalue_flag = 0 if allvalue==0
gen allvalue_log=log(allvalue + 1)
gen allpr_log=log(allpr + 1)
gen income_log=log(income + 50)
gen homevalue_log=log(homevalue + 1)
summarize allvalue_flag allvalue_log allpr_log income_log homevalue_log
```

keep relevant features
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
keep resp1pid age gender education egp hukou party familysize income_log homevalue_log isei allvalue_flag allvalue allpr allvalue_log allpr_log gdp
```

Save the final data
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
codebook, compact
save "data\family_merged_tidy.dta", replace
```


## Exploratory analysis in R

I like ggplot so I'll just insert some R code chunks to visualize some exploratory analysis.

Setup
```{r packages, include=FALSE}
# Load packages.
packages <- c("tidyverse",
              "knitr",
              "finalfit",
              "ggplot2",
              "gridExtra",
              "FactoMineR",
              "factoextra"
              )
packages <- lapply(packages, FUN = function(x) {
  if(!require(x, character.only = TRUE)) {
    install.packages(x)
  library(x, character.only = TRUE)
  }
}
)
```

load the new dataset in r
```{r}
cfps<-haven::read_dta(file = "data/family_merged_tidy.dta")
```

Some new categorical features
```{r}
#Function to recode numeric variables to factor with 5 levels according to top values
recode_numeric <- function(var, prefix = "", tile = 0.9) {
  top1 <-
    quantile(var, tile, na.rm = TRUE)#First group by default is top 10%
  top2 <- top1 * 2 / 3#Bottome line of second group is 2/3 of first one
  top3 <- top2 / 2#Next group's bottom line is 1/2 of previous
  top4 <- top3 / 3#Next group's bottom line is 1/3 of previous
  var <- var %>% cut(
    breaks = c(-Inf, top4, top3, top2, top1, Inf),
    labels = c(
      str_c("v.low.", prefix, collapse = ""),
      str_c("low.", prefix, collapse = ""),
      str_c("mid.", prefix, collapse = ""),
      str_c("high.", prefix, collapse = ""),
      str_c("v.high.", prefix, collapse = "")
    )
  )
  return(var)
}
```

Convert to factors
```{r}
cfps <- cfps %>% mutate(
  age_group = recode_numeric(age),
  familysize_group = recode_numeric(familysize),
  isei_group = recode_numeric(isei),
  allvalue_log_group = recode_numeric(allvalue_log),
  income_log_group = recode_numeric(income_log),
  homevalue_log_group = recode_numeric(homevalue_log)
)

for (i in names(cfps)){
  cfps[[i]]<-cfps[[i]]%>%as.factor()
}
```

### Visualize relationship between variables

51% in the data has no expense on leisure.

```{r}
#construct summary statistics by education, profit, martial status etc. to set up ggplot data infrastructure
hukou.plot <- ggplot(
  data = cfps %>% group_by(hukou, allvalue_flag) %>% summarise(percent =
                                                                        n() * 100 / nrow(cfps)) %>% mutate(group = str_c(hukou, " and leisure", allvalue_flag)),
  aes(x = hukou,
      y = percent,
      fill = allvalue_flag)
)

party.plot <- ggplot(
  data = cfps %>% group_by(party, allvalue_flag) %>% summarise(percent =
                                                                        n() * 100 / nrow(cfps)) %>% mutate(group = str_c(party, " and leisure", allvalue_flag)),
  aes(x = party,
      y = percent,
      fill = allvalue_flag)
)

age_group.plot <- ggplot(
  data = cfps %>% group_by(age_group, allvalue_flag) %>% summarise(percent =
                                                                        n() * 100 / nrow(cfps)) %>% mutate(group = str_c(age_group, " and leisure", allvalue_flag)),
  aes(x = age_group,
      y = percent,
      fill = allvalue_flag)
)

education.plot <- ggplot(
  data = cfps %>% group_by(education, allvalue_flag) %>% summarise(percent =
                                                                        n() * 100 / nrow(cfps)) %>% mutate(group = str_c(education, " and leisure", allvalue_flag)),
  aes(x = education,
      y = percent,
      fill = allvalue_flag)
)

#my function to make the plots and make them prettier
formatting <- function(plot, legend = FALSE) {
  plot <- plot +
    geom_bar(stat = "identity") +
    scale_fill_brewer(palette = "Paired") +
    ylab("") +
    labs(fill = "Have leisure expense")  +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1))+
    theme(text = element_text(size = 20))
  if (legend == FALSE) {
    plot <- plot +
      theme(legend.position = "none")
  }
  return(plot)
}

#combine the 4 plots together in 1 page
grid.arrange(
  hukou.plot %>% formatting(),
  party.plot %>% formatting(),
  age_group.plot %>% formatting(),
  education.plot %>% formatting(legend = TRUE),
  left = "Percentage"
)
```

We can see older people, people without urban residence status, non-party members and people with less education generally tend to be more conservative on leisure expenses.

### MCA with categorical variables
```{r}
#MCA based on the data
cfps_mca <- cfps %>% select(
  age_group,
  gender,
  familysize_group,
  hukou,
  party,
  education,
  allvalue_flag,
  isei_group,
  allvalue_log_group,
  income_log_group,
  homevalue_log_group
)
mca <- MCA(
  cfps_mca,
  ncp = 5,
  method = "Burt",
  graph = FALSE
)
```

```{r}
#Visualize MCA outcome
fviz_mca_var(
  mca,
  axes = c(1, 2),
  choice = "var.cat",
  repel = TRUE,
  map = "symmetric",
  shape.var = "circle",
  col.var = "orange2",
  col.quali.sup = "black"
) +
  ggtitle("Relationship between categorical variables",
          subtitle = "Multiple Correspondence Analysis with Burt Method") +
  labs(caption = "Source: CFPS2016") +
  theme_classic() +
  theme(text = element_text(size = 20))
```

On top right We can see those who spend more on leisure usually have more wealth, more education, better occupations; but on the left part of X axis, those with no expense on leisure tend to be less educated, have large family size, originate from rural areas, etc.

```{r}
#Plot contribution of variables of first dimension
contrib.plot1 <- fviz_contrib(
  mca,
  choice = "var",
  axes = 1,
  sort.val = "desc",
  top = 10
) +
  xlab("variable group") +
  labs(caption = "Source: Multiple Correspondence Analysis based on CFPS") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))+
  theme(text = element_text(size = 20))
#Plot contribution of variables of second dimension
contrib.plot2 <- fviz_contrib(
  mca,
  choice = "var",
  axes = 2,
  sort.val = "desc",
  top = 10
) +
  xlab("variable group") +
  labs(caption = "Source: Multiple Correspondence Analysis based on CFPS") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))+
  theme(text = element_text(size = 20))
#Show together
grid.arrange(contrib.plot1,
             contrib.plot2,
             ncol = 1)
```

## Modeling
### Missing value handling

Missingness overview
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
use "data\family_merged_tidy.dta", replace
ssc install mdesc
mdesc
```

visualize missing patterns
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
misstable patterns egp isei education
```

t-test of target variable between missing/non missing parts of variables
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
foreach var of varlist egp isei education{
  gen `var'_flag=1
  replace `var'_flag=0 if `var'==.
  ttest income_log, by(`var'_flag)
}
```

The occupation info should be MNAR
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
* recoded into extreme values
recode isei .=9999
recode egp .=9999
```

Turns out education might be MAR
```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
* imputed with mice along with other vars
mi set mlong
mi register imputed income_log hukou education homevalue_log
mi impute mvn income_log hukou education homevalue_log = age gender familysize party, add(5) rseed (0)
```

### Logit model 
Among elder people>60, build a regession on the likelihood of someone has any expense on leisure, seperating "have" from "have-not"s. On top of other variables, increasing age introduce a decreasing likelihood spending on leisure.

```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
mi estimate: logit allvalue_flag age gender familysize hukou isei party education income_log homevalue_log if age > 60
```

### OLS model
Among those who spend on leisure, another OLS look at factors contributing to how much is spent on leisure

```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
mi estimate: regress allvalue_log age gender familysize hukou isei party education income_log homevalue_log gdp if allvalue_log>0 & age > 60
```

Same formulation targeting at the proportion of leisure of total consumption

```{stata, collectcode=TRUE, echo=FALSE, cleanlog=FALSE}
mi estimate: regress allpr_log age gender familysize hukou isei party education income_log homevalue_log gdp if allpr_log>0 & age > 60
```

Age remain significant in both equations, showing that elder people that are more senior will tend to not only less likely to spend but also spend less on leisure. The interpretation will be based on the fact that these people in the Chinese society suffer from hunger in childhood therefore exhibit a habitus that is more necessity-based. More illustrations in the paper. 
