---
title: "R to Excel"
author: "Langyi Tian"
date: "March 2020"
output: html_document 
--- 

## Setup
```{r setup, include=FALSE}
rm(list = ls())#clear environment
wd <- "~/GitHub/Pet-projects/r-to-excel/"#set working directory
#Set up default knitr chunk options
library("knitr")
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE, 
  cache = TRUE,
  cache.lazy = FALSE
) 
```   

```{r load packages}
packages <- c(
  "tidyverse",
  "openxlsx",
  "lubridate",
  "finalfit"
)
packages <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x)
      library(x, character.only = TRUE)
    }
  }
)
select<-dplyr::select
```

## Data exploration
```{r}
#import raw data
addsToCart <- read.csv("addsToCart.csv",
                  stringsAsFactors = FALSE)
sessionCounts <- read.csv("sessionCounts.csv",
                  stringsAsFactors = FALSE)
```

By a quick glance at the input and desired output, 
1. The "Month * Device" sheet is a summary of metrics in sessionCounts data by month (date) and device. 
2. Further summarizing the previous sheet, the "Month Summary" sheet is by month only, merged with addsToCart data.
So the process would proceed timely according to the order.

```{r}
#print a summary
summary(sessionCounts)
```
There might exist some anomalies (how come a device can have 43k sessions in a day?), but without subjective domain knowledge we'll keep them raw now.

```{r}
#check missing values
missing_glimpse(sessionCounts)
```
No missing value imputation needed.

```{r}
#Engineer the month variable
sessionCounts <-
  sessionCounts %>% mutate(dim_month = month(dim_date %>% as.Date()))#round date to month
sessionCounts$dim_month %>% summary()
```

## make the month device sheet
```{r}
#make the month device sheet
month_device <-
  sessionCounts %>% #take this data
  group_by(Month = dim_month, `Device Category` = dim_deviceCategory) %>% #group by month and category
  summarise(
    Sessions = sum(sessions),
    Transactions = sum(transactions),
    QTY = sum(QTY),
  ) %>% #compute summary statistics
  mutate(ECR = Transactions / Sessions) %>% #compute ECR
  arrange(Month, `Device Category`) # arrange by month then device

month_device
```

## make the month summary sheet
```{r}
#modify names of addtocard data
names(addsToCart)<-c("Month","Adds To Cart")

#make the month summary sheet
month_summary <-  month_device %>%
  group_by(Month) %>% #group by month
  summarize(
    Sessions = sum(Sessions),
    Transactions = sum(Transactions),
    QTY = sum(QTY)
  ) %>% #print summary stats
  mutate(ECR = Transactions / Sessions,
         `Device Category` = "Overall") %>% #compute metrics again
  full_join(addsToCart, by = "Month") %>% #join with add to cart data
  select(Month,
         `Device Category`,
         Sessions,
         Transactions,
         QTY,
         `Adds To Cart`,
         everything()) %>% #reorder variables
  arrange(Month) #arrange by month
month_summary
```

## create the excel dashboard
```{r}
#create a new wb
wb <- createWorkbook()
#create new sheets
addWorksheet(wb, "Month x Device")
addWorksheet(wb, "Month Summary")
#write data into sheet
writeData(wb, "Month x Device", month_device)
writeData(wb, "Month Summary", month_summary)
#create headline style
hs <- createStyle(wrapText = TRUE,
                  textDecoration = "BOLD", 
                  border = "bottom",
                  fgFill = "#E5E5E5")
#add hs
addStyle(wb,sheet = 1,hs,rows = 1, cols = 1:6)
addStyle(wb,sheet = 2,hs,rows = 1, cols = 1:7)
#set column width
setColWidths(wb, sheet = 1, cols = 1:6, widths = 11)
setColWidths(wb, sheet = 2, cols = 1:7, widths = 11)
#not show grid lines
showGridLines(wb, 1, showGridLines = FALSE)
showGridLines(wb, 2, showGridLines = FALSE)
#save workbook
saveWorkbook(wb, "workbook-from-r.xlsx", overwrite = TRUE)
```
